\documentclass[11pt]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace}
\RequirePackage{tikz, pgflibraryplotmarks}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amsthm, amssymb}
\newtheorem{thm}{{\bf Theorem}}
\newtheorem{lemma}{{\bf Lemma}}
\newcommand{\A}{\mathfrak{A}}
\theoremstyle{definition}
\newtheorem{define}{Definition}
\newtheorem{claim}{Claim}
\newtheorem*{method}{Method}
\newtheorem{ex}{Example}
\newcommand{\dydx}{\dfrac{dy}{dx}}
\newcommand{\dydt}{\dfrac{dy}{dt}}
\newcommand{\dxdt}{\dfrac{dx}{dt}}
\newcommand{\dxdy}{\dfrac{dx}{dy}}
\newcommand{\pp}{\prime\prime}
\newcommand{\p}{\prime}
\renewcommand{\d}[2]{\dfrac{d#1}{d#2}}
\newcommand{\dd}[2]{\dfrac{d^2#1}{d#2^2}}
\newcommand{\ypp}{y^{\prime\prime}}
\newcommand{\ds}{\displaystyle}
\newcommand{\yp}{y^{\prime}}
\renewcommand\thesection{2.5}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{lipsum}% Used for dummy text.
\usepackage{enumerate}

% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{MTH130}
\newcommand{\term}{Fall 2018}
\newcommand{\examnum}{Practice Exam 1}
\newcommand{\examdate}{Oct. 11th}
\newcommand{\timelimit}{75 Minutes}

% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule
 {\bf \class} \hfill  \textbf{Name:\underline{\hspace{2in}}}\\
\ \\
 {\bf \examnum} \hfill  \textbf{Section:\underline{\hspace{2in}}}\\

\rule[1ex]{\textwidth}{.1pt}


This exam contains \numpages\ pages (including this cover page) and
\numquestions\ problems.  Check to see if any pages are missing.  Enter
all requested information on the top of this page, and put your initials
on the top of every page, in case the pages become separated.\\

You may \textit{not} use your books, notes, or any calculator on this exam.\\

You are required to show your work on each problem on this exam.  The following rules apply:\\

\begin{minipage}[t]{3.7in}

\begin{itemize}
\item \textbf{Organize your work}, in a reasonably neat and coherent way, in
the space provided. Work scattered all over the page without a clear ordering will 
receive very little credit.  

\item \textbf{Mysterious or unsupported answers will not receive full
credit}.  A correct answer, unsupported by calculations, explanation,
or algebraic work will receive no credit; an incorrect answer supported
by substantially correct calculations and explanations might still receive
partial credit.

\item If you need more space, ask for an extra sheet of paper to continue the problem on; clearly indicate when you have done this.
\end{itemize}

{\bf Do not write in the table to the right.}
\end{minipage}
\hfill
\begin{minipage}[t]{2.3in}
\vspace{0pt}
\cellwidth{3em} %cellwidth
\gradetablestretch{2}%some sort of stretching of the table
\vqword{Problem}
\addpoints % required here by exam.cls, even though questions haven't started yet.	
\gradetable[v]%[pages]  % Use [pages] to have grading table by page instead of question
\end{minipage}
\newpage % End of cover page


\begin{questions}
\addpoints
\question[7]Find the indicated limits if they exist. 
\begin{enumerate}[a)]

\item $\ds \lim_{x\rightarrow 0}\dfrac{2x^2-3x}{x}$
\vfill
\item $\ds \lim_{x\rightarrow -4}\dfrac{x+13}{x+4}$
\vfill
\item $\ds \lim_{x\rightarrow -5}\sqrt[3]{2x+2}$
\vfill
\item $\ds\lim_{x\rightarrow 3} \dfrac{x^2-9}{x-3}$
\vfill
\item $\ds\lim_{x\rightarrow \infty} \dfrac{x^2}{x^2+1}$
\vfill
\item $\ds\lim_{x\rightarrow \infty} \dfrac{2x^2-1}{x+1}$
\vfill
\item $\ds\lim_{x\rightarrow \infty} \dfrac{6x^2+2x-2}{x^4+2x+1}$
\end{enumerate}
\newpage
\addpoints
\question[4] Consider the function below. 
\[f(x)=\frac{(x-1)(x+2)(2x-3)}{(x+2)(x-3)(x+1)}\]
Find the vertical asymptotes, horizontal asymptotes, and the points of discontinuities. \\
\vspace{.25in}
\begin{enumerate}[\ ]
\item {\bf Vertical Asymptotes: }
\vspace{.5in}
\item {\bf Horizontal Asymptotes:}
\vspace{.5in}
\item {\bf Points of Discontinuities:}
\vfill
\end{enumerate}
\addpoints
\question[3] Find the derivatives of the following functions.
\begin{enumerate}[a)]
\item $f(x)=6,393$
\vfill
\item $f(x)=3x^2+3x^2+5x+1$
\vfill
\item $f(x)=8x^2+\frac{1}{x^5}$
\vfill
\end{enumerate}
\addpoints
\question[3] Use the product and quotient rules to find the derivatives of the following functions.
\begin{enumerate}[a)]
\item $f(x)=(2x+5)(x^3+1)$
\vfill
\item $f(x)=\dfrac{x^2+1}{3x+2}$
\vspace{.15in}
\end{enumerate}

\newpage
\addpoints 
\question[4] Find the derivative of the following functions 
\begin{enumerate}[a)]
\item $f(x)=\sqrt{x^3+2x+1}$
\vfill
\item $f(x)=\dfrac{(x+3)^3}{2x}$
\vfill
\end{enumerate}
\question[4] Consider the function below. 
\[f(x)=x^2+3x+1\]
\begin{enumerate}[a)]
\item Find the average rate of change of the function over $[1,2]$
\vfill
\item Find the tangent line at the point $(1,5)$. 
\vfill
\end{enumerate}








\end{questions}
\end{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic question
\addpoints
\question[10] Differentiate $f(x)=x^2$ with respect to $x$.

% Question with parts
\newpage
\addpoints
\question Consider the function $f(x)=x^2$.
\begin{parts}
\part[5] Find $f'(x)$ using the limit definition of derivative.
\vfill
\part[5] Find the line tangent to the graph of $y=f(x)$ at the point where $x=2$.
\vfill
\end{parts}

% If you want the total number of points for a question displayed at the top,
% as well as the number of points for each part, then you must turn off the point-counter
% or they will be double counted.
\newpage
\addpoints
\question[10] Consider the function $f(x)=x^3$.
\noaddpoints % If you remove this line, the grading table will show 20 points for this problem.
\begin{parts}
\part[5] Find $f'(x)$ using the limit definition of derivative.
\vspace{4.5in}
\part[5] Find the line tangent to the graph of $y=f(x)$ at the point where $x=2$.
\end{parts}