\documentclass[11pt ]{article}
\usepackage{amsmath, amssymb, enumerate, amsthm}
\usepackage[margin=0.75in]{geometry}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\usepackage{pdflscape}
\thispagestyle{empty}
\begin{document}
\begin{landscape}
{\noindent \Huge \bf Grading Rubric}
\begin{flushleft}
\def \arraystretch{1.15}
\begin{tabular}{|l|p{0.21\textwidth} | p{0.21\textwidth} | p{0.21\textwidth} | p{0.21\textwidth} |}\hline
Category & 4 & 3 & 2 & 1\\
\hline
Mathematics & Demonstrates a complete understanding. & Demonstrates an adequate understanding. & Demonstrates a partial understanding. & Unsatisfactory understanding of material.\\
\hline
Vocabulary & Skillful use of vocabulary. & Adequate use of vocabulary. &  Vague use of vocabulary.& Incorrect use of vocabulary.\\
\hline
Organization & Clear and logical idea progression. Easy to follow. & Adequate and logical idea progression. Generally easy to follow. & Weak idea progression and difficult to understand. & No idea progression and difficult to understand. Incomplete sentences.\\
\hline
Grammar & Meaning of writing is
very clear with only one
reading. Generally free
of most errors & Meaning of writing is
mostly clear with only
one reading. Some errors. & Meaning of writing is
interrupted with only one
reading. Accumulation of
errors & Meaning of writing is
constantly disrupted
with only one
reading. Pervasive
errors\\
\hline
\end{tabular}
\end{flushleft}
\ \\
\begin{minipage}{.5\textwidth}
{\bf \Large Other Notes:}
\begin{enumerate}[1.]
\item Paper must have a bibliography/citations.
\item Single spaced, 3-4 pages typed. 
\item Questions to ask yourself:
\begin{enumerate}[$\square$]
\item Is there a logical development of concepts?
\item Does the paper provide examples?
\item Does the paper contain all the necessary definitions?
\item Is all the information correct?
\item Are all the theorems and proofs mathematically correct?
\item Does the paper give evidence that you understand the material?
\item Is the paper organized, free of grammar and spelling errors, and have smooth transitions?
\end{enumerate}
\end{enumerate}
\end{minipage}
\hspace{2in}
\begin{minipage}{.5\textwidth}
{\bf \Large Possible topics:}
\begin{enumerate}[1.]
\item Riemann rearrangement theorem. 
\item Picard Lindel\"{o}f Theorem and ODE's
\item Convex functions
\item Hilbert spaces
\item Fourier series
\item Topology 
\item Newtons Method
\item Nowhere differentiable functions. 
\item Construction of the Real numbers. 
\item You may also pick your own topic. Please discuss with me to see if its appropriate.
\end{enumerate}
\end{minipage}
\end{landscape}
\end{document}